The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-01-17 SC-challenge.tex
Suggested citations
If we cite it people might use it?

Modern science and engineering depend on software. 
To acknowledge traditional research results published in archival journals and conferences, we use citation, but no such accepted standard exists to credit the considerable efforts that go into software.
One method to increase the amount of software developed, shared and credited is to treat a software release as a publication. 
In addition, since research results, including data, now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
\textbf{The main challenge of software citation is that we need a way to uniquely identify released (published) software so that it can be cited by others who use it.}
We also need a process to curate and review software.

@@

Multiple groups, including the WSSSPE Software Credit~\cite{WSSSPE1,WSSSPE2,WSSSPE3} and FORCE11 Software Citation Working Groups, are working to standardize citation practices; some of the observations and recommendations made here come from these groups.
Our efforts follow similar work by DataCite and the FORCE11 Data Citation Synthesis Group~\cite{DataCitation2014} to standardize research data citation practices.
Currently, services including Zenodo or fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process to register DOIs for GitHub software releases.
The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemas in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).

>>>>

Modern science and engineering depend on software. 
To acknowledge traditional research results published in archival journals and conferences, we use citation, but no such accepted standard exists to credit the considerable efforts that go into software.
One method to increase the amount of software developed and shared is to treat a software release as a publication. 
In addition, since research results, including data, now depend on the specific software used (e.g., version), proper citation---and the associated preservation---is necessary to ensure reproducibility.
\textbf{The main challenge of software citation is that we need a way to uniquely identify released (published) software so that it can be cited by others who use it.}
We also need a process to curate and review software.

@@

Multiple groups, including the WSSSPE Software Credit~\cite{WSSSPE1,WSSSPE2,WSSSPE3} and FORCE11 Software Citation Working Groups, are working to standardize citation practices; some of the observations and recommendations made here come from these groups.
Our efforts follow similar work by DataCite and the FORCE11 Data Citation Synthesis Group~\cite{DataCitation2014} to standardize research data citation practices.
Currently, services including Zenodo or fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process to register DOIs for GitHub software releases.
Currently, services including Zenodo or fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process~\cite{GitHubZenodo} to register DOIs for GitHub software releases.
The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemes in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).
